\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-08 manuscript/main.tex
update the robustness check

>>>>

\subsection{Additional Robustness Check for the Offline Expansion Effect} \label{subsec:expansion_effect}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect}
      \label{tab:robustness_check_additional_1}
      \input{../result_tables/entry_robust_adding_variables_1.tex}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Offline Expansion Effect (Continued)}
      \label{tab:robustness_check_additional_2}
      \input{../result_tables/entry_robust_adding_variables_2.tex}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect}
      \label{tab:robustness_check_platform_1}
      \input{../result_tables/plat_robust_adding_variables_1.tex}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect (Continued)}
      \label{tab:robustness_check_platform_2}
      \input{../result_tables/plat_robust_adding_variables_2.tex}
